---
title: "Statistical Inference Week4 Peer Graded Assignment"
author: "Sandip Khanvilkar"
date: "May 20, 2018"
output:pdf_document:
df_print: paged
pdf_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/skhanvilkar/Statistical Inference/")
set.seed(20000)
```
##**Introduction:** 
The project consists of two parts:
A simulation exercise.
Basic inferential data analysis.
A pdf report will be created using knitr which will detail out all the answers to the series of questions. 

##**Data:** 
The simulated data have been used for this assignment. 

##**Section 1: Simulation Exercise Instructions**  
This section will investigate the exponential distribution in R and compare it with the Central Limit Theorem. The exponential distribution is simulated in R with rexp(n, lambda) 
where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda, where lambda = 0.2 for all of the simulations. The distribution is investigated of averages of 40 exponentials.  
#**Question 1: To show the sample mean and compare it to the theoretical mean of the distribution.** 
```{r}
n <- 40
Simulations <- 1000
Lambda <- 0.2

SampleMean <- NULL
for(i in 1:Simulations) {
  SampleMean <- c(SampleMean, mean(rexp(n, Lambda)))
}
mean(SampleMean)       
```
*So, as we can see, compared to the theoretical mean distribution of 5 , our mean 5 is close. 
#**Question 2: Show and compare it to the theoretical variance of the distribution.** 
*The theoretical standard deviation of the distribution is also 1/lambda , which, for a lambda of 0.2 , equates to 5 . The variance is the square of the standard deviation, which is 25.*
```{r}
Variance <- var(SampleMean)
```
*0.5 is close to the theoretical distribution.* 
##*Show that the distribution is appoximately normal*  
```{r}
hist(SampleMean, breaks = n, prob = T, col = "maroon", xlab = "Means")
x <- seq(min(SampleMean), max(SampleMean), length = 100)
lines(x, dnorm(x, mean = 1/Lambda, sd = (1/Lambda/sqrt(n))), pch = 25, col = "yellow")
```
```{r}
qqnorm(SampleMean)
qqline(SampleMean, col = "blue")
```
#*QQ Plot suggests that the distribution averages of 40 exponentials is very close to a normal distribution.* 

##**Section 2: Basic Inferential Data Analysis Instructions**  
This section will investigate the analysis of ToothGrowth data.

###**Step 1: Load the ToothGrowth data.** 
library(knitr)
opts_chunk$set(echo = TRUE, results = "markup", warning = TRUE, cache = TRUE, tidy = FALSE)
```{r}
library(datasets)
data(ToothGrowth)
library(ggplot2)
```
###**Step 2:Provide the basic summary data and perform exploratory analysis.**
```{r}        
str(ToothGrowth)
head(ToothGrowth)
summary(ToothGrowth)
```
```{r}
ggplot(data=ToothGrowth, aes(x=as.factor(dose), y=len, fill=supp)) +
    geom_bar(stat="identity") +
    facet_grid(. ~ supp) +
    xlab("Dose(mg)") +
    ylab("Tooth length")
```


###**Step 3:Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.**  
```{r}  
hypoth1 <- t.test(len ~ supp, data = ToothGrowth)
hypoth1$conf.int
```
```{r} 
hypoth1$p.value
```
```{r} 
hypoth2<-t.test(len ~ supp, data = subset(ToothGrowth, dose == 0.5))
hypoth2$conf.int
```
```{r} 
hypoth3<-t.test(len ~ supp, data = subset(ToothGrowth, dose == 1))
hypoth3$conf.int
```
```{r} 
hypoth3$p.value
```
```{r} 
hypoth4<-t.test(len ~ supp, data = subset(ToothGrowth, dose == 2))
hypoth4$conf.int
```
```{r} 
hypoth4$p.value
```
##**Conclusion:** 
OJ ensures more tooth growth than VC for dosages 0.5 & 1.0. OJ and VC givesthe same amount of tooth growth for dose amount 2.0 mg/day. For the entire trail we cannot conclude OJ is more effective that VC for all scenarios.
